---
title: "Example Article"
output: 
  rmarkdown::html_document:
    toc: true
    toc_title: "Content"
    source: false
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

> **Template Users:** This is an example article showing how to create pkgdown articles. Replace this content with your own topic-specific documentation. Articles are perfect for tutorials, case studies, and supplementary documentation that doesn't fit in standard vignettes.

## What Are pkgdown Articles?

Articles are a special type of documentation in pkgdown that differ from standard vignettes:

- **Vignettes** (in `vignettes/`) are included in the package installation and available via `browseVignettes()`
- **Articles** (in `vignettes/articles/`) are only published on your pkgdown website, not in the installed package

### When to Use Articles

Use articles for:

- **Tutorials** that require large datasets or external resources
- **Case studies** with extensive examples
- **Supplementary documentation** that's too detailed for vignettes
- **Web-only content** like interactive visualizations or external API examples

## Example: Using the Template Package

This template includes an example function `lm_model()` that demonstrates best practices:

```{r}
library(blankpkg)

# Load example data
data(dummy_df)

# Fit a linear model using the template's example function
model <- lm_model(
  df = dummy_df,
  response = "a",
  predictors = c("b", "c", "d")
)

# View model summary
summary(model)
```

### Code Structure

The example shows several best practices:

1. **Input validation** - The function checks that inputs are valid
2. **Flexible parameters** - Users can specify response and predictors
3. **Informative errors** - Clear error messages guide users
4. **Comprehensive documentation** - Full roxygen2 documentation with examples

## Creating Your Own Articles

When customizing this template:

1. **Delete this example article** or use it as a reference
2. **Create new articles** for your package's specific use cases
3. **Organize articles** by topic in `_pkgdown.yml`:

```yaml
articles:
  - title: "Getting Started"
    navbar: ~
    contents:
    - intro
  - title: "Advanced Topics"
    navbar: Advanced
    contents:
    - advanced-usage
    - performance-tips
```

4. **Build your site** with `source("dev/pkgdown_build_site.R")`

## Tips for Writing Articles

- **Use clear section headings** for easy navigation
- **Include working code examples** that readers can copy-paste
- **Add visualizations** when helpful (plots, diagrams, tables)
- **Link to function documentation** using `` `function_name()` ``
- **Keep it focused** - one article per topic

## Further Reading

- [pkgdown Articles Documentation](https://pkgdown.r-lib.org/articles/pkgdown.html#articles)
- [R Markdown Guide](https://rmarkdown.rstudio.com/lesson-1.html)
- See `dev/README.md` for all development scripts, including `pkgdown_build_site.R`

---

**Remember:** This is example content for the template. Replace it with documentation specific to your package's functionality!
